Interval Probability for Fuzzy Quantum Theories

### 2016-07-18 prob.tex
prob.tex \subsection{Interval-valued probability measures} expending a footnote...

\begin{example}[Two-coin experiment with interval probability]
  \label{ex3} We split the unit interval $[0,1]$ in the following four
  closed sub-intervals: $[0,0]$ which we call \imposs,
  $[0,\frac{1}{2}]$ which we call \unlikely, $[\frac{1}{2},1]$ which
  we call \likely, and $[1,1]$ which we call \necess. Using these new
  values, we can modify the probability measure of Ex.~\ref{ex1} by
  mapping each numeric value to the smallest sub-interval containing
  it to get the following:
\[
\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\bar{\mu}(\emptyset) & = & \imposs\\
\bar{\mu}(\{HH\}) & = & \unlikely\\
\bar{\mu}(\{HT\}) & = & \imposs\\
\bar{\mu}(\{TH\}) & = & \likely\\
\bar{\mu}(\{TT\}) & = & \imposs\\
\bar{\mu}(\{HH,HT\}) & = & \unlikely\\
\bar{\mu}(\{HH,TH\}) & = & \necess\\
\bar{\mu}(\{HH,TT\}) & = & \unlikely
\end{array} & \begin{array}{rcl}
\bar{\mu}(\{HT,TH\}) & = & \likely\\
\bar{\mu}(\{HT,TT\}) & = & \imposs\\
\bar{\mu}(\{TH,TT\}) & = & \likely\\
\bar{\mu}(\{HH,HT,TH\}) & = & \necess\\
\bar{\mu}(\{HH,HT,TT\}) & = & \unlikely\\
\bar{\mu}(\{HH,TH,TT\}) & = & \necess\\
\bar{\mu}(\{HT,TH,TT\}) & = & \likely\\
\bar{\mu}(\{HH,HT,TH,TT\}) & = & \necess
\end{array}\end{array}
\]
Despite the absence of any numeric information, the probability
measure is quite informative: it reveals that the second coin is
double-headed and that the first coin is biased. To understand the
$\subseteq$-condition, consider the following calculation:
\begin{eqnarray*}
 &  & \bar{\mu}(\{HH\})+\bar{\mu}(\{HT\})+\bar{\mu}(\{TH\})+\bar{\mu}(\{TT\})\\
 & = & \imposs+\unlikely+\imposs+\likely\\
 & = & \left[0,0\right]+\left[0,\frac{1}{2}\right]+\left[0,0\right]+\left[\frac{1}{2},1\right]=\left[\frac{1}{2},\frac{3}{2}\right]
\end{eqnarray*}
If we were to equate $\bar{\mu}(\Omega)$ with the sum of the individual
probabilities we would get that
$\bar{\mu}(\Omega) = \left[\frac{1}{2},\frac{3}{2}\right]$. However,
using the fact that $\bar{\mu}(\emptyset)=\imposs$, we have
$\bar{\mu}\left(\Omega\right)=1-\bar{\mu}\left(\emptyset\right)=\necess=[1,1]$. This
interval is tighter and a better estimate for the probability of the
event $\Omega$ and of course it is contained in
$[\frac{1}{2},\frac{3}{2}]$. However it is only possible to exploit
the information about the complement when all four events are
combined. Thus the $\subseteq$-condition allows us to get an estimate
for the combined event from each of its constituents and then gather
more evidence knowing the aggregate event.\qed\end{example}
\footnote{\yutsung{The Radon-Nikodym Theorem for interval-valued
probability?\cite{GilboaSchmeidler1994}?}}

>>>>

\begin{example}[Two-coin experiment with interval probability]
  \label{ex3} We split the unit interval $[0,1]$ in the following four
  closed sub-intervals: $[0,0]$ which we call \imposs,
  $[0,\frac{1}{2}]$ which we call \unlikely, $[\frac{1}{2},1]$ which
  we call \likely, and $[1,1]$ which we call \necess. Using these new
  values, we can modify the probability measure of Ex.~\ref{ex1} by
  mapping each numeric value to the smallest sub-interval containing
  it to get the following:
\[
\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\bar{\mu}(\emptyset) & = & \imposs\\
\bar{\mu}(\{HH\}) & = & \unlikely\\
\bar{\mu}(\{HT\}) & = & \imposs\\
\bar{\mu}(\{TH\}) & = & \likely\\
\bar{\mu}(\{TT\}) & = & \imposs\\
\bar{\mu}(\{HH,HT\}) & = & \unlikely\\
\bar{\mu}(\{HH,TH\}) & = & \necess\\
\bar{\mu}(\{HH,TT\}) & = & \unlikely
\end{array} & \begin{array}{rcl}
\bar{\mu}(\{HT,TH\}) & = & \likely\\
\bar{\mu}(\{HT,TT\}) & = & \imposs\\
\bar{\mu}(\{TH,TT\}) & = & \likely\\
\bar{\mu}(\{HH,HT,TH\}) & = & \necess\\
\bar{\mu}(\{HH,HT,TT\}) & = & \unlikely\\
\bar{\mu}(\{HH,TH,TT\}) & = & \necess\\
\bar{\mu}(\{HT,TH,TT\}) & = & \likely\\
\bar{\mu}(\{HH,HT,TH,TT\}) & = & \necess
\end{array}\end{array}
\]
Despite the absence of any numeric information, the probability
measure is quite informative: it reveals that the second coin is
double-headed and that the first coin is biased. To understand the
$\subseteq$-condition, consider the following calculation:
\begin{eqnarray*}
 &  & \bar{\mu}(\{HH\})+\bar{\mu}(\{HT\})+\bar{\mu}(\{TH\})+\bar{\mu}(\{TT\})\\
 & = & \imposs+\unlikely+\imposs+\likely\\
 & = & \left[0,0\right]+\left[0,\frac{1}{2}\right]+\left[0,0\right]+\left[\frac{1}{2},1\right]=\left[\frac{1}{2},\frac{3}{2}\right]
\end{eqnarray*}
If we were to equate $\bar{\mu}(\Omega)$ with the sum of the individual
probabilities we would get that
$\bar{\mu}(\Omega) = \left[\frac{1}{2},\frac{3}{2}\right]$. However,
using the fact that $\bar{\mu}(\emptyset)=\imposs$, we have
$\bar{\mu}\left(\Omega\right)=1-\bar{\mu}\left(\emptyset\right)=\necess=[1,1]$. This
interval is tighter and a better estimate for the probability of the
event $\Omega$ and of course it is contained in
$[\frac{1}{2},\frac{3}{2}]$. However it is only possible to exploit
the information about the complement when all four events are
combined. Thus the $\subseteq$-condition allows us to get an estimate
for the combined event from each of its constituents and then gather
more evidence knowing the aggregate event.\qed\end{example}

Because a probability measure~$\pmeas:\events\rightarrow[0,1]$ can
be simplified to its Radon-Nikodym derivative~$\rho:\Omega\rightarrow[0,1]$
by the Radon-Nikodym theorem, people have tried to find a Radon-Nikodym
Theorem for the interval-valued probability measure. One possible
approach is to consider the inverse Möbius transform of $\bar{\mu}:\events\rightarrow\mathscr{I}$~\cite{GilboaSchmeidler1994,Goodman2013}.
Although the inverse Möbius transform can always be defined, the domain
of the inverse Möbius transform of of $\bar{\mu}$ is still the event
space~$\events$ so that it does not simplify an interval-valued
probability measure to a function from the same space~$\Omega$.
The other approach tried to only consider the Radon-Nikodym derivative
between two interval-valued probability measures with a special relation
called the strong decomposition property~\cite{Choquet1954,Graf1980,Goodman2013}.
However, only the real-valued probability measures could have a Radon-Nikodym
derivative with respect to the counting measure\footnote{\yutsung{Need to verify a concrete example.}}.
In summary, there is no satisfactory Radon-Nikodym Theorem to simplify
interval-valued probability measures~$\bar{\mu}:\events\rightarrow\mathscr{I}$
to their Radon-Nikodym derivative~$\bar{\rho}:\Omega\rightarrow\mathscr{I}$.
